Graph bipartitioning and you

### 2015-12-08 evolutionaryComputation/2-practical/report.tex
name of the report

\newcommand{\brcell}[2][l]{%
	\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
\begin{document}
\begin{empfile}
\begin{empcmds}
input metauml;
\end{empcmds}
\author{Jappie Klooster}
\title{A practical look at genetic algorithms}
\maketitle

\section{Introduction}
This is a report of the evolutionary practical assignment 1.
In here I will discuss the execution of the assignment, what it was, which
methodology was used to execute the assignment.

@@

\section{Assignment}
The assignment was to implement the following functions and algorithms and
then do experimentation with help of these.

\subsection{Functions}
\subsubsection{Counting functions}
\[x_i \in \{0,1\}:CO(x_1\dots x_l)=\sum^l_{i=1}x_i\]
\[x_i \in \{0,1\}:CO(x_1\dots x_l)=\sum^l_{i=1}i x_i\]
\subsubsection{Trap function}
\[TF(x_1\dots x_l) = \sum^{\frac{l}{k}-1}_{j=0}B(x_{jk_1}\dots x_{jk+k})\]

with:

\[B(x_1\dots x_k)=\left\{
	\begin{matrix}
		k & \mbox{ if } &   CO(x_1\dots x_k) = k \\
		k - d - \frac{k-d}{k-1} CO(x) & \mbox{ if } & CO(x_1\dots x_k) < k \\
	\end{matrix}
\right. \]

\subsection{Experiment}
After implementing these functions we were tasked to make an experiment of it
and make some graphs of the results and make a conclusion based on the results.

>>>>

\newcommand{\brcell}[2][l]{%
	\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
\begin{document}
\begin{empfile}
\begin{empcmds}
input metauml;
\end{empcmds}
\author{Jappie Klooster}
\title{Graph bipartitioning and you}
\maketitle

\section{Introduction}
This is a report of the evolutionary practical assignment 2.
In here I will discuss the execution of the assignment, what it was, which
methodology was used to execute the assignment.

@@

\section{Assignment}
Graphbipartitioning is dividing a graph into 2, with as little edges between
both graphs as possible.
